---
title: "App's Reproducible Pitch"
author: "Shivam"
date: "10 Sept, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About the App

The link to the app is [here](https://rajputshivam1415.shinyapps.io/myapp/)

The app uses the data set provided in the r package `datasets` and takes in an input of the variables to be taken in the x and y axis of the plots to be plotted.  <br/>
It takes in the values and produces 3 types of plots, <br/>
1. The first one labeled Plot produces a type "o" plot from the function of x and y variables  <br/>
2. The second one labeled Regression Plot first plots the points selected and then adds a fitted regression line to it and also shows the summary of the linear model included  <br/>
3. The third one shows a box plot of the taken variables (It will show an error if you choose the same variables in both the plots, so please try and select different variables)  <br/>

The app also shows a small description about the data set

## Regression Model Example Using Sepal Length and Species

```{r}
library(datasets)
data("iris")
fit <- lm(Sepal.Length ~ Species, data = iris)
coef(summary(fit))
```

## Boxplot Example with Petal Width and Sepal Width

```{r}
boxplot(Sepal.Width ~ Petal.Width, data = iris)
```

## Thank You